
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENTS}

% Schael, Wiebusch
First, I would like to thank Prof. Dr. Stefan Schael for giving me the opportunity to work in his institute as a member of the AMS-02 collaboration. During the last few years, I have always benefited from his supervision and guidance. His passion for physics and his enthusiasm have really inspired me. Moreover, I have learned a lot from his ambition to push things forward. I would also like to thank Prof. Dr. Christopher Wiebusch for agreeing to be my second supervisor for the thesis. \par

% Ting
Secondly, I would like to thank Prof. Samuel Ting, the Primary Investigator of the whole AMS-02 experiment. Without his effort in the last decades, the AMS-02 project would not have come true. His spirit of never giving up will inspire me in the future. In addition, I admire his concentration and perseverance throughout his career.   \par

% Aachen colleagues
Many friends and colleagues helped me a lot during my PhD time in Aachen. Special thanks to Robin Sonnabend who helped me from zero ground when I was a beginner in AMS. He is always patient to teach me and answer stupid questions. I would like to thank Dr. Henning Gast. As the actual host in the Aachen analysis group, he put a lot of effort to support the Aachen data analysis. \par

During my PhD study in the institute, many friends and colleagues have made my working time pleasant: Dr. Nikolas Zimmermann, Dr. Bastian Beischer, Dr. Fabian Machate, Dr. Nikolay Nikonov, Dr. Leila Ali Cavasonza, Dr. Sofia Chouridou, Manbing Li, Emiliano Rampi, and Yasaman Najafi. I have always learned a lot from the discussions with you, and the time I spent with you guys will always be a precious memory for me. 

I would like to thank again Dr. Henning Gast and Dr. Sofia Chouridou who did proofreadings for this thesis. Many thanks for your time and valuable comments. \par  

I would like to thank Dr. Georg Schwering, Natalie Driessen, Tanja Bingler and Gina Wilden for their support work in the administration branch of the institute. As a foreigner working in Aachen, I was guided by them in almost every step of my PhD program.  \par

% CERN
During my shifts at CERN, many friends and colleagues there made my stay enjoyable. I would like to thank Dr. Mike Capell, Dr. Zhili Weng, Dr. Weiwei Xu, Dr. Valery Zhukov, Dr. Youmin Yu, Dr. Baosong Shan, Dr. Yi Jia, Dr. XiaoTing Qin and so many other people. The discussions we had at the POCC had always made my time there delightful.   \par

% Family
Last but foremost, I would like to thank my family. Their continuous love and encouragement are the sources of power for me that support me all the time. This thesis wouldn't have been possible without your support. 

